---
title: "Apriori algorithm in Groceries dataset"
output:
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
    theme: simplex
    social: menu
    source_code: embed
---


```{r setup, include=FALSE}
library(RColorBrewer)
library(data.table)
library(dplyr)
library(ggplot2)
library(knitr)
library(stringr)
library(DT)
library(plotly)
library(arules)
library(arulesViz)
library(visNetwork)
library(igraph)
library(kableExtra)
```

# About Groceries Dataset


### Dataset Description
```{r}
print("The Groceries data set contains 1 month (30 days) of real-world point-of-sale transaction data from a typical local grocery outlet. The data set contains 9835 transactions and the items are aggregated to 169 categories.")

```
Link to [Statistical Inference]

# Statistical Inference

Column {data-width=500}
-----------------------------------------------------------------------

### DataStructure
```{r}
d = data("Groceries")
str(Groceries)
```

### Transaction
```{r}
inspect(head(Groceries))
```



Column {data-width=500}
-----------------------------------------------------------------------


### Summary
```{r}
summary(Groceries)
```

### Length of transactions

```{r}
length(head(transactions))
```


Link to [Apriori Algorthm]

# Apriori Algorthm
Column {data-width=500}
-----------------------------------------------------------------------

### Apply apriori algorthm
```{r}
rules=apriori(Groceries, parameter = list(support = 0.002,confidence=0.5))
```



###One-dimensional tables
```{r}
head(round(itemFrequency(Groceries),3))
head(itemFrequency(Groceries,type='absolute'))
```
###Two - dimensional tables
```{r}
cctab=crossTable(Groceries, measure='count',sort=TRUE)
head(round(cctab))
```

###support measure
```{r}
stab=crossTable(Groceries, measure='support',sort=TRUE)
head(round(stab,1))
```

###Left measure
```{r}
ltab=crossTable(Groceries, measure='lift',sort=TRUE)
head(round(ltab,1))
```



Link to [About Groceries Dataset]

Column {data-width=500}
-----------------------------------------------------------------------
### Distribution of transaction

```{r}
groceries_trans=as(Groceries,"transactions")
hist(size(groceries_trans),breaks=15,main="Transaction Length Distribution",xlab="Transaction Length")

```

### Frequent itemset
```{r}
arules::itemFrequencyPlot(Groceries, topN = 10, 
                          col = brewer.pal(8, 'Pastel2'),
                          main = 'Frequent Items',
                          type = "relative",
                          ylab = "Item Frequency (Relative)")
```

### Creating rules
```{r}
rules.groc=apriori(Groceries, parameter=list(support=0.006,confidence=0.25,minlen=2))
```

### Sorting rules by count
```{r}
rules.cou=sort(rules.groc,by='count',decreasing=TRUE)
inspect(head(rules.cou))
```


### Sorting rules by confidence
```{r}
rules.con=sort(rules.groc,by='confidence',decreasing=TRUE)
inspect(head(rules.con))
```

### Sorting rules by lift
```{r}
rules.lif=sort(rules.groc,by='lift',decreasing=TRUE)
inspect(head(rules.lif))
```

### rules check
```{r}
inspect(rules.groc)
```


### Confidence of the groceries
```{r}
inspect(sort(sort(rules, by ="support"),by ="confidence")[1:5])
plot(rules, measure=c("support", "confidence"), shading="lift", interactive=FALSE)
```


### igraph view

```{r}
itemset=eclat(Groceries, parameter = list(support=0.02,minlen=2))
plot(itemset,method="graph")

```

